---
filters:
  - _extensions/pandoc-ext/section-bibliographies/section-bibliographies.lua
reference-section-title: References
bibliography: inst/docs/bibliography.bib
---

```{r}
#| echo: false
source("inst/docs/_common.R")
.gh_url <- file.path('https://github.com', rmarkdown::metadata[['github-repo']])
```

# Welcome {-}

This is the landing page of the `BiocBook` entitled ...  
This book introduces the reader to key concepts in ...   

`r rebook::openingDetails(Source=.gh_url)`

# Reproducibility {-}

This `BiocBook` has been written using the 
[`BiocBook` package](https://github.com/js2264/BiocBook) from `Bioconductor`, 
and also relies on other packages, including (but not only): 

- `devtools`
- `quarto`
- `rebook`

To build this book locally, you can run: 

```{sh eval = FALSE, filename="bash"}
git clone git@github.com:js2264/OHCA.git && cd OHCA
quarto render
```

::: {.callout-warning}
All dependencies listed above will be required!
:::

The actual rendering of this book is done by GitHub Actions, and the 
rendered static website is hosted by GitHub Pages. 

## Session info {-}

```{r}
#| echo: false
#| results: "hide"
#| message: false
#| warning: false
library("HiCExperiment")
library("HiCool")
library("HiContacts")
library("HiContactsData")
library("fourDNData")
library("DNAZooData")
library("OHCA")
```

```{r}
sessioninfo::session_info()
```
