# Containerize and Publish against specific Bioconductor release versions

## For a `BiocBook` package not currently in Bioconductor

One can build against older Bioconductor releases as follows: 

- Commit current changes before switching branches (should be in `devel` branch)

```{r}
gert::git_commit_all("Commit current changes")
```

- Create a new branch named `RELEASE_X_Y` and checkout

```{r}
gert::git_branch_create("RELEASE_3_17")
```

- Push local `RELEASE_X_Y` to Github

```{r}
gert::git_push()
```

## For a `BiocBook` package accepted in Bioconductor > 6 months ago

Once your package is accepted in Bioconductor, your repository will have 
access to a new **remote** named `upstream`, pointing to `git@git.bioconductor.org`. 
When Bioconductor releases a new version, your package will change version on 
the `upstream` remote, in a dedicated release branch `RELEASE_X_Y`. 
All details are available [here](https://contributions.bioconductor.org/git-version-control.html). 

To generate a Docker image and a version of the `BiocBook` website built 
on new Bioconductor releases, you can: 

- Add the `Bioconductor` remote to your local repository (this might already be set up)

```{r}
gert::git_remote_add(name = 'upstream', url = 'git@git.bioconductor.org:packages/<YOUR-REPOSITORY>.git')
```

- Create a new local `RELEASE_X_Y` branch 

```{r}
gert::git_branch_create("RELEASE_3_15")
```

- Pull the `upstream` `RELEASE_X_Y` commits

```{r}
gert::git_pull("RELEASE_3_15", remote = "upstream")
```

- Push the local `RELEASE_X_Y` branch to `origin` remote (your own Github repository)

```{r}
gert::git_push("RELEASE_3_15", remote = "origin")
```

