# Writing a `BiocBook` package

## Register a Github account in R

::: {.callout-info icon='true'}

Skip this section if your `git` credentials and Github account are already 
registered. You can check this by typing: 

```{r}
#| eval: false
usethis::git_sitrep()
```

:::

::: {.callout-warning icon='true'}

### Both `git` and Github credentials must be set up!

:::

Don't forget to select whichever setting 
is best-suited for you in the `Expiration` dropdown menu!

```{r}
#| eval: false
## ------ Indicate git login details 
gert::git_config_global_set("user.name", "Bobby")
gert::git_config_global_set("user.email", "bobby@cat.com")

## ------ Create a new Github token
usethis::create_github_token(
    description = "BiocBook", 
    scopes = c("repo", "user", "gist", "workflow", "write:packages")
)
## Select an Expiration date 
## Click on "Generate token" at the bottom of the page
## Copy your Github token displayed in the Github web page

## ------ Register your new token in R
gitcreds::gitcreds_set()
## Paste your new Github token here and press "Enter"

## ------ Double check you are logged in
usethis::git_sitrep()
```

You may also want to add your Github token to `~/.Renviron` to save it for 
futur use. You can edit the `~/.Renviron` by typing `usethis::edit_r_environ()`, 
and the following environment variable should be created: 

```{txt filename="~/.Renviron"}
GITHUB_PAT="<YOUR-TOKEN>"`
```

## Initiate a `BiocBook` package

::: {.panel-tabset group="tools-tabset"}

### R console

```{r}
#| eval: false
BiocBook_init("BiocBook")
```

### From GitHub

#### Use the `BiocBook.template` package template {-}

#### Clone it locally {-}

#### Edit placeholders where needed! {-}

:::

## Add new `BiocBook` pages

- New chapters can be created with `add_chapter(biocbook, file, title)`; 
- `add_preamble(biocbook)` is used to add an unnumbered extra page after the Welcome 
page but before the chapters begin; 

## Writing features 

### Executing code

It's super easy to execute actual code from any `BiocBook` page when rendering the `BiocBook` website. 

#### `R` code

`R` code can be executed and rendered: 

```{r filename="R"}
utils::packageVersion("BiocVersion")
```

#### `bash` code

`bash` code can also be executed and rendered: 

```{sh filename="bash"}
find ../ -name "*.qmd"
```

<!-- 
#### `python` code

Finally, `python` code can also be executed and rendered: 

```{python filename="python"}
#| eval: false
import os
os.getcwd()
```

For the rendering of `python` code, you will be limited to 
the `python` packages installed in the Github worker. These packages can be 
listed in the `inst/assets/requirements.txt` file, e.g.: 

```{txt filename="requirements.txt"}
#| eval: false
numpy
pandas >= 2.0.0
```
 -->

### Adding references

References can be listed as `.bib` entries in the bibliography file located in 
`inst/assets/bibliography.bib`. The references can be added in-line using the @ notation, 
e.g. by typing **\@serizay2023**, this will insert the following reference: **@serizay2023**. 
